---
title: "A Shiny App"
author: "Mary T."
date: "October 8, 2017"
output: ioslides_presentation
---

## Social Media Facts

- Today around seven-in-ten Americans use social media to connect with one another, engage with news content, share information and entertain themselves.
- According to the Pew Research Center social media adoption by American adults has increased from 5% in 2005 to over 70% today. (http://www.pewinternet.org/fact-sheet/social-media/).
- Young adults were among the earliest social media adopters and continue to use these sites at high levels, but usage by older adults has increased in recent years.
- This application looks at the data trends by age and gender.
- It also calculates a non-scientific loss of productivity (years) based on gender and hours spent on social media.

## Data structure

```{r, echo = FALSE}
age_SM <- read.table("age_SM.txt", header = TRUE)
age_SM$Period <- as.Date(age_SM$Period, format = "%m / %d / %Y")

gender_SM <- read.table("gender_SM.txt", header = TRUE)
gender_SM$Period <- as.Date(gender_SM$Period, format = "%m / %d / %Y")

```

```{r echo = TRUE}
str(age_SM)

```

```{r echo = TRUE}
str(gender_SM)

```


## Data summary

```{r echo = TRUE}
head (age_SM, 5)
head (gender_SM, 5)

```


## Application
<iframe 
  src="https://mst0722.shinyapps.io/Survey_app/" 
  allowfullscreen> </iframe>
